---
output: 
  github_document:
    toc: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rsegregation

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/arthurgailes/rsegregation.svg?branch=master)](https://travis-ci.org/arthurgailes/rsegregation)
<!-- badges: end -->

rsegregation is designed to fit into the tidyverse framework, particularly dplyr.

## Installation
<!--
You can install the released version of rsegregation from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rsegregation")
```
-->
The development version from [GitHub](https://github.com/) can be installed with:

``` {r eval=FALSE}
  # install.packages("devtools")
  devtools::install_github("arthurgailes/rsegregation")
# dplyr is also suggested
# install.packages('dplyr')
```

## Usage

Return a single divergence score for bay County:

```{r example, results='hide}
library(rsegregation)
library(dplyr)
## basic example code
bay_divergence <- bay_race %>% 
  mutate(bay_divergence = divergence(white,black,asian, hispanic, all_other), summed = T)
```

### Base R Example

The same operation can be achieved in base R with:

```{r baser1}
bay_divergence <- divergence(bay_race[c('white','black','asian', 'hispanic', 'all_other')], 
  summed = T)
```

or

```{r baser2}
bay_divergence <- divergence(bay_race$white,bay_race$black,bay_race$asian, 
  bay_race$hispanic, bay_race$all_other, summed = T)
```

```{r echo=FALSE, results=TRUE}
print(bay_divergence)
```




### Misc

Dataframes should be formatted as long on geographic observations (e.g. tracts), but wide on group observations (e.g. races), as in the included dataset of bay County, CA

```{r bay, eval=FALSE}
head(bay_wide)
```

### Split-Apply-Combine

rsegregation supports group_by %>% summarize operations from the dplyr package.
```{r}

```

