---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rsegregation

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/arthurgailes/rsegregation.svg?branch=master)](https://travis-ci.org/arthurgailes/rsegregation)
<!-- badges: end -->

This package is designed to fit into the tidyverse framework, particularly dplyr.

## Installation
<!--
You can install the released version of rsegregation from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rsegregation")
```
-->
The development version from [GitHub](https://github.com/) can be installed withwith:

``` {r eval=FALSE}
# install.packages("devtools")
devtools::install_github("arthurgailes/rsegregation")
# dplyr is also recommended
# install.packages('dplyr')
```

## Usage

Return a single divergence score for bay County:

```{r example, eval=FALSE}
library(rsegregation)
library(dplyr)
## basic example code
bay_divergence <- bay_race %>% 
  mutate(bay_divergence = divergence(white,black,asian))
  
```

## Base R Example

The same operation can be achieved in base R with:

```{r baser}
summary(cars)
```

### Misc

Dataframes should be formatted as long on geographic observations (e.g. tracts), but wide on group observations (e.g. races), as in the included dataset of bay County, CA

```{r bay, eval=FALSE}
head(bay_wide)
```

### Split-Apply-Combine

rsegregation supports group_by %>% summarize operations from the dplyr package.
```{r}

```

