---
output: 
  github_document:
    df_print: kable
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rsegregation

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/arthurgailes/rsegregation.svg?branch=master)](https://travis-ci.org/arthurgailes/rsegregation)
[![Codecov test coverage](https://codecov.io/gh/arthurgailes/rsegregation/branch/master/graph/badge.svg)](https://codecov.io/gh/arthurgailes/rsegregation?branch=master)
[![R build status](https://github.com/arthurgailes/rsegregation/workflows/R-CMD-check/badge.svg)](https://github.com/arthurgailes/rsegregation/actions)
<!-- badges: end -->

rsegregation is designed to fit into the tidyverse framework, particularly dplyr.

## Installation
<!--
You can install the released version of rsegregation from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rsegregation")
```
-->
The development version from [GitHub](https://github.com/) can be installed with:

``` {r eval=FALSE}
  # install.packages("devtools")
  devtools::install_github("arthurgailes/rsegregation")
```

## Usage

rsegregation depends upon dplyr (>1.0.0), and can be used with it. To return a single divergence score for Bay Area County:

### Divergence and Entropy

#### Calculate the divergence score for the entire dataset

rsegregation can work with base r, or within several dplyr verbs:
```{r bay_divergence, results='hide'}
library(rsegregation)
library(dplyr)
## included dataset of Bay Area Census tracts
# Using dplyr
bay_divergence <- bay_race %>% 
  summarize(bay_divergence = divergence(white,black,asian, hispanic, all_other), summed = T)

# Using base r
bay_divergence <- divergence(bay_race[c('white','black','asian', 'hispanic', 'all_other')], 
  summed = T)
# or
bay_divergence <- divergence(bay_race$white,bay_race$black,bay_race$asian, 
  bay_race$hispanic, bay_race$all_other, summed = T)
# all return the same result:
bay_divergence
```

#### Calculate divergence by group

Using the included Bay Area dataset of 2010 racial groups, divergence can be calculated by county using `dplyr::group_by()`.
```{r by_county}
#library(dplyr)
group_by(bay_race, county) %>% 
  summarize(bay_divergence = divergence(white,black,asian, hispanic, all_other, summed = T))
```

#### By-observation divergence scores
Divergence and entropy are both calculated rowwise by default (summed = FALSE).
```{r by_tract}
bay_entropy <- bay_race
bay_entropy$entropy <- entropy(bay_race[c('white','black','asian',
  'hispanic','all_other')], summed = F)
head(bay_entropy)
```

### Miscellaneous

Dataframes should be formatted as long on geographic observations (e.g. tracts), but wide on group observations (e.g. races), as in the included dataset of the San Francisco Bay Area.

```{r bay}
head(bay_race)
```


## Future development:
 
* decomposition of entropy index
* more measures of segregation

## License
This package is free and open source software, licensed under GPL-3. 
