---
title: "Replicating Segregation Papers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{replication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette reproduces the results of some popular segregation packages.

```{r setup}
library(rsegregation)
library(dplyr, warn.conflicts = FALSE)
```

#### The Divergence Index: A Decomposable Measure of Segregation and Inequality

In [this paper](https://arxiv.org/abs/1508.01167), Elizabeth Roberto calculates divergence and entropy scores for the city of Detroit. Her calculations compare the black and white population specifically.

*Load Data*

```{r}
load(system.file('extdata','detroit_race.rda', package='rsegregation', mustWork = T))


# get black/white specific stats
detroit_mod <- detroit_race %>%
    filter(population>0) %>%
    mutate(pop_bw=population*(black+white), black_bw=black/(black+white),
      white_bw=white/(black+white))
```

*Divergence Index*

```{r}
# Roberto's results
robCity <- 0.14
robMetro <- 0.48

city <- dplyr::filter(detroit_mod, grepl('Detroit',place_name))

# compare city black/white results
city_bw <- summarize(city, div=divergence(black_bw, white_bw,
  population=pop_bw, summed=T, logBase=2))
expect_equivalent(city_bw$div, robCity, tolerance=0.01)

# compare metro results
metro_bw <- summarize(detroit_mod, div=divergence(black_bw, white_bw,
  population=pop_bw, summed=T, logBase=2))
expect_equal(metro_bw$div, robMetro, tolerance=0.01)
```

*Entropy/Information Theory Indexes*

Entropy has several scores, comparing them here.
```{r}
# compare city black/white results
  create_comp <- function(df) summarize(df, ent=entropy(black_bw, white_bw,
    population=pop_bw, summed=T, logBase=2),
    inf=entropy(black_bw, white_bw, entropy_type = 'information_theory',
      population=pop_bw, summed=T, logBase=2))
  city_bw <- create_comp(city)
  expect_equivalent(city_bw$ent, 0.29, tolerance=0.01)
  expect_equivalent(city_bw$inf, 0.32, tolerance=0.01)

  # compare metro results
  metro_bw <- create_comp(detroit_mod)
  expect_equal(metro_bw$ent, 0.33, tolerance=0.01)
  expect_equivalent(metro_bw$inf, 0.59, tolerance=0.01)
```

