---
title: "R Notebook"
---

Trial and error tests with log base (groups) vs natural log.

```{r}
devtools::load_all()
```

Test the difference between total and black/white segregation using ln and base(groups)
```{r}
# test the difff between ln and log(groups)

detroit_mod <- detroit_race %>%
  mutate(newrace=NA_real_, white_bw = white/(white+black), black_bw=black/(white+black),
    pop_bw = population*(white+black)) %>%
  summarize(
    divln = divergence(across(black:hispanic), population=population, summed=T),
    divln1 = divergence(white_bw, black_bw, population=pop_bw, summed=T),
    divbase = divergence(across(black:hispanic), population=population, logBase=4, summed=T),
    divbase1 = divergence(white_bw, black_bw, newrace, population=pop_bw, logBase=2, summed=T))
detroit_mod

t <- detroit_race %>%
  select(-tract) %>%
  mutate(place_name = ifelse(grepl('Detroit',place_name), place_name,'Other'))
decompose_divergence(t, groupCol='place_name',popCol='population', output='all')

decompose_divergence(t, groupCol='place_name',popCol='population', output='all', logBase=6)

```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
